Wrangle transcripts

### 2025-10-23 code/demog.qmd
data prep and more annotation

>>>>

# expt 3

```{r}

expt_3_demog <- read_csv(here("expt_3_demog.csv"))

expt_3 <- read_csv(here("data/expt_3/clean_data.csv")) |>
  select(game = gameId, speaker, listener) |>
  pivot_longer(c("speaker", "listener"), values_to = "sid") |>
  select(-name) |>
  unique() |> 
  mutate(expt=3)

expt_3_demog <- read_csv(here("expt_3_demog.csv")) |> 
 mutate(
    date_test = mdy(date_test),
    date_birth = ymd(date_birth)
  ) |>
  select(sid=SID, date_test, date_birth, hispanic, ethnicity, gender) |> 
  full_join(expt_3) |> 
  filter(!is.na(game)) |> 
  mutate(
    age_days = (date_test - date_birth) |> as.numeric(),
    age_month = floor(age_days / 30.43)
  ) |>
  select(-age_days) |>
  mutate(id=sid) |> 
  select(expt, game, id, sid, gender, age_month, ethnicity, hispanic) |> write_csv(here("data/clean_demog_3.csv"))

```

### 2025-10-23 code/expt_3/data_prep_3.Rmd
data prep and more annotation

raw_data |>
  filter(!is.na(repNum)) |>
  filter(submitted == "true") |>
  group_by(gameId) |>
  tally()

@@

wrangle_transcript <- function(game_num) {
  read_xlsx(here("data/expt_2/raw_transcripts", str_c(game_num, ".xlsx"))) |>
    select(start, end, text, speaker, trial, role, echo, description) |>
    fill(trial) %>%
    mutate(start = start / 1000, end = end / 1000) |>
    mutate(trial = as.character(trial)) |>
    nest(data = c(start, end, text, speaker, trial, role, echo, description))
}

transcripts <- read_csv(here("data/expt_2/link_transcripts.csv")) |>
  select(gameId, gameConfig) |>
  mutate(transcript = map_df(gameConfig, wrangle_transcript)) |>
  unnest(transcript) |>
  unnest(data)

write_csv(transcripts, here("data/expt_2/transcripts.csv"))
```

@@

```{r}
transcript <- read_csv(here("data/expt_2/transcripts.csv"))

dat <- read_csv(here("data/expt_2/clean_data.csv")) %>% select(trial = trialNum, gameId, target, distractor)
transcript %>%
  filter(!is.na(description)) %>%
  group_by(trial, gameId) %>%
  mutate(trial = as.numeric(trial)) |>
  filter(trial > 3) |>
  summarize(words = str_c(description, sep = " ", collapse = ", ")) %>%
  left_join(dat) %>%
  write_csv(here("data/expt_2/pre_sbert.csv"))
```

```{r}
library(reticulate)
np <- import("numpy")
mat <- np$load(here("data/expt_2/post_sbert.npy"))
saveRDS(mat, here("data/expt_2/post_sbert.RData"))
```

```{r}
sbert <- read_csv(here("data/expt_2/pre_sbert.csv")) %>% bind_cols(read_rds(here("data/expt_2/post_sbert.RData")) %>%
  as_tibble())

@@

similarities <- M_mat %>%
  mutate(combinedId = str_c(gameId, trial, sep = "_")) %>%
  make_across_df(F_mat, "cosine") %>%
  separate(dim1, into = c("game1", "trial1"), convert = T, sep = "_") %>%
  separate(dim2, into = c("game2", "trial2"), convert = T, sep = "_") %>%
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  write_rds(here("data/expt_2/similarities.rds"))
```

>>>>

@@

wrangle_transcript <- function(game_num) {
  read_tsv(here("data/expt_3/raw_transcripts", str_c(game_num, ".tsv"))) |>
    select(start, end, text, speaker, trial, role, echo, description) |>
    fill(trial) %>%
    mutate(start = start / 1000, end = end / 1000) |>
    mutate(trial = trial-1) |>
    nest(data = c(start, end, text, speaker, trial, role, echo, description))
}

transcripts <- read_tsv(here("data/expt_3/link_transcripts.csv")) |> 
  select(gameId, gameConfig) |>
  mutate(transcript = map_df(gameConfig, wrangle_transcript)) |>
  unnest(transcript) |>
  unnest(data)

write_csv(transcripts, here("data/expt_3/transcripts.csv"))
```

@@

```{r}
transcript <- read_csv(here("data/expt_3/transcripts.csv"))

dat <- read_csv(here("data/expt_3/clean_data.csv")) %>% select(trial = trialNum, gameId, target, distractor)
transcript %>%
  filter(!is.na(description)) %>%
  group_by(trial, gameId) %>%
  mutate(trial = as.numeric(trial)) |>
  filter(trial > 3) |>
  summarize(words = str_c(description, sep = " ", collapse = ", ")) %>%
  left_join(dat) %>%
  write_csv(here("data/expt_3/pre_sbert.csv"))
```

```{r}
library(reticulate)
np <- import("numpy")
mat <- np$load(here("data/expt_3/post_sbert.npy"))
saveRDS(mat, here("data/expt_3/post_sbert.RData"))
```

```{r}
sbert <- read_csv(here("data/expt_3/pre_sbert.csv")) %>% bind_cols(read_rds(here("data/expt_3/post_sbert.RData")) %>%
  as_tibble())

@@

similarities <- M_mat %>%
  mutate(combinedId = str_c(gameId, trial, sep = "_")) %>%
  make_across_df(F_mat, "cosine") %>%
  separate(dim1, into = c("game1", "trial1"), convert = T, sep = "_") %>%
  separate(dim2, into = c("game2", "trial2"), convert = T, sep = "_") %>%
  mutate(sim = ifelse(is.nan(sim), NA, sim)) %>%
  write_rds(here("data/expt_3/similarities.rds"))
```
